Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-28 doc/JFLA2022/paper.tex
minor change

\section{Modernizing the infrastructure}
\subsection{Documentation with Alectryon}
\begin{todo}
  Interest of Alectryon:
  \begin{itemize}
  \item Despite the frequent changes (improvements) in the Coq scripts, code inclusion and \textit{Coq}'s answers are up to date.

  \item Presentation of the main steps of proofs, possibly interleaved with text.
  \item \TODO[Clément]{A good part of the LaTeX support in Alectryon was developed for hydra-battles, and this was the first real application with a custom driver, too.}
  \item \TODO[Clément]{If you kept a trace of them, I would love to see a discussion of any errors that were caught by including the output systematically instead of copy-pasting it.}
  \item \TODO[Pierre]{the order of appearance of snippets in the book is independent from the module structure}
   \item \TODO[Pierre]{Slicing our proofs into snippets allowed to show only the main parts of our proofs (Figure~\ref{fig:Ex42-schutte}).}

>>>>

\section{Modernizing the infrastructure}
\subsection{Documentation with Alectryon}
\begin{todo}
  Interest of Alectryon:
  \begin{itemize}
  \item Despite the frequent changes (improvements) in the Coq scripts, code inclusion and \textit{Coq}'s answers are up to date.
  \item \TODO[Clément]{A good part of the LaTeX support in Alectryon was developed for hydra-battles, and this was the first real application with a custom driver, too.}
  \item \TODO[Clément]{If you kept a trace of them, I would love to see a discussion of any errors that were caught by including the output systematically instead of copy-pasting it.}
  \item \TODO[Pierre]{the order of appearance of snippets in the book is independent from the module structure}
   \item \TODO[Pierre]{Slicing our proofs into snippets allowed to show only the main parts of our proofsleaved with text (Figure~\ref{fig:Ex42-schutte}).}
